\chapter{North County Rules and Procedures}
\label{chap:rules}
\section{Rule ``A'': League Schedules}
\subsection{Section 1}
\begin{enumerate}[A.]
    \item League winners are determined by the total number of points accrued.  Points are determined as follows:
    \begin{center}
        \begin{tabular}{ l r }
            Result & Points \\
            \hline
            Win & 2 \\
            Tie & 1 \\
            Loss & 0 \\
        \end{tabular}
    \end{center}
    \item “A” League teams that are tied at the end of the season must play a tie-breaking game/match. If more than two (2) teams are tied, there will be a single elimination playoff established by the Chairperson. Use of a coin toss or 	draw of lots will be used to determine the pairings.
    
    “B” League teams that are tied at the end of the season will be crowned Champions and share first place.  Each team will be given individual trophies, if applicable.   

    \item Definitions
    \begin{enumerate}[1.]
        \item Division  -  A division is a grouping of teams by age and/or talent levels.
        
        Examples - Girls Midget A (GMA), Midget B1 (GMB1), Boys Intermediate Open (BIO), Boys Intermediate A (BIA), Boys Junior (BJR).

        \item League  -  A league is any four teams assembled to play together on a schedule (page) for a sport season.  A league must have at least four (4) teams and can have one (1) or more divisions.
    \end{enumerate}
\end{enumerate}

\subsection{Section 2}
No league will be larger than ten (10) teams.  Exception:  Juvenile and Junior Divisions.

\section{Rule ``B'': Adult Participation Requirements}
\subsection{Section 1}
\begin{enumerate}[A.]
    \item For the purpose of this rule, an adult is considered to be a person who is at least 21 years of age.
    \item Each team should have at least One (1) adult meeting the coaching requirements on the roster. One (1) adult, with an ID card, must be in attendance, on the bench and be responsible for the teams’ actions during the entire game, or the game will be subject to forfeited.  It is required that a second adult, with the same, be present on the bench or sideline.
\end{enumerate}

\section{Rule ``C'': Communications}
The manager's line of communication to the North County CYC Athletic Association is through his/her Parish Representative. League business, such as scheduling, rescheduling, scoring, standing issues, etc. are to be directed to his/her League Coordinator.

\section{Rule ``D'': Program Improvement}
Constructive criticism is an asset to any program, provided it is handled by the persons in charge and with an open mind.  It is recommended that any constructive suggestions for improvement in our program be submitted to your Parish Representative, so that they may be presented at an Executive Board Meeting.  An individual submitting such criticism should have a feel for the overall situation and recommend a solution to the problem.

\section{Rule ``E'': Scorecards}
\subsection{Section 1}
After the game, an official will present the scorecard to each manager for his/her signature and approval of the final score. The official score shall be as shown on the scorecard.  All blanks shall be recorded as zero (0).  Should an error be made, and the Athletic Association desires a correction, the Parish Representative must submit an official Score Card Correction Request form to the Vice Chairperson.  The Vice Chairperson will verify said information with both managers and the League Coordinator.

\subsection{Section 2}
Comments regarding game officials should be made on an Incident and presented to your Parish Representative.

\section{Rule ``F'': Uniform Colors}
The following list contains the uniform colors assigned to each parish in the North County CYC Athletic Association.  If conflict in colors exists, the team in violation, or the Home Team, must correct the problem.  For any variation in colors listed, permission must be received from the District Executive Board.  NOTE:  If soccer or basketball teams with the same primary colors are playing each other, the Home team is responsible for resolving the conflict, i.e., supply pennies.

\begin{center}
    \begin{tabular}{l l}
        Parish & Colors \\
        \hline
        St. Ann & Navy/Gold \\
        Sacred Heart & White/Red \\
        St. Norbert & Columbia Blue/Navy Blue \\
        Christ Light of Nations & Red/Blue \\
        Blessed Teresa & Royal Blue/White \\
        St. Sabina & Maroon/Gold \\
        St Angela Merici & Gold/Green \\
        Our Lady of Guadalupe & Kelly Green/Gold \\
        St. Martin de Porres & Gold/Black \\
        St. Ferdinand & Royal Blue/Gold \\
        St. Rose & Red/Black \\
        \hline
    \end{tabular}
\end{center}

Teams playing out of color may be subject to forfeiture.
               
\section{Rule ``G'': General Information/Duties}
\label{sec:rules-g}
\subsection{Section 1: Parish Representative}
\begin{enumerate}[A.]
    \item The Parish Representative has a delicate position to maintain:
    \begin{enumerate}[1.]
        \item Represent the desires of his/her athletic association and must vote in the manner prescribed by his/her athletic association.
        \item Maintain strict enforcement of the Executive Board's policies.
        \item Assume a share of the Executive Board's duties in each sport.
        \item Inform their athletic association personnel of any new policy or policy change initiated by the Executive Board.
        \item Review rosters submitted by his/her athletic association to assure accuracy of information, especially verifying Parish of Registration and the indication of.
        \item Assure that rosters are completed and filed by the designated date with the District Vice Chairperson.
        \item Assure that Team Entry Forms properly reflect the information needed by the Screening Committee and are turned in to the Vice Chairperson when requested by the District Constitution.
        \item Instruct your athletic association on the correct procedure, whether it be rosters, roster changes, protests, request for scheduling, etc.
        \item Provide the District Vice Chairperson with a list of parish/athletic association activities prior to/at the Screening Meeting for each sport.
        \item Keep a current list of athletic association personnel and provide the names and phone numbers of the Sport Coordinators.   Coordinator information must be provided not later than:
        \begin{center}
            \begin{tabular}{l l}
                Meeting & Sport \\
                \hline
                February EBM & Baseball / Softball \\
                June EBM & Soccer / Volleyball \\
                September EBM & Basketball \\
                \hline
            \end{tabular}
        \end{center}
        \item Act as/perform the duties of a League Coordinator
        \item Perform additional tasks as required; deemed necessary through the course of business.
    \end{enumerate}
    \item The Parish Representative, in his/her absence, may designate an alternate to fulfill his/her duties, with all rights and privileges.  Notification must be provided to the Chairperson/Vice Chairperson.
\end{enumerate}

\subsection{Section 2: League Coordinator}
\begin{enumerate}[A.]
    \item Must maintain communications with managers of their assigned leagues with respect to scores and win/loss   record and cancellations. 
    \item Notify the District Vice Chairperson of the need to reschedule games for the following reasons:
    \begin{enumerate}[1.]
        \item Rainouts
        \item Incomplete games (called due to darkness, weather conditions, etc).
        \item Reasons listed in By-Law XIV.
    \end{enumerate}
    \item Attempt to attend games in his/her assigned leagues to observe the conduct of players, coaches, managers, spectators and officials, and in general, the conduct of the contest.
\end{enumerate}

\subsection{Section 3: Duties of the Officers}
\subsubsection{A. District Chairperson}
\begin{enumerate}[1.]
    \item Plan the season and plan ahead for each sport.
    \item Understand that the job is very time consuming.
    \item Keep the Parish Representatives informed of all pertinent matters.
    \item Be diplomatic at all times.
    \item May request advice on policies from the Board of Control, then enforce them to the best of your ability.
    \item Despite the trials and tribulations of the job, the Chairperson has the responsibility of setting a good example of leadership without bias.
    \item Approve expenditures and expenses, holding them to a minimum.
    \item Represent the North County District at the monthly meetings of the Archdiocesan Executive Sports Committee.
    \item Serve as Chairperson of the Board of Control.
    \item Appoint the Secretary, Treasurer, Sergeant at Arms, and Special Advisor(s) for their terms of service.
    \item Take reschedule requests from the Vice Chairperson and determine if a reschedule is to be granted.
    \item Chair the monthly District Executive Board meeting.
    \item Hold meetings with the parish sport coordinators 6 weeks prior to start of sport season, as required during the sport season.
    \item Assemble the Spirit of St. Louis Tournament rosters and submit to the CYC Office.
    \item Assemble the Spirit of St. Louis Tournament shirt order and submit to the CYC Office.
    \item Notify the District league winners and inform them about the Archdiocesan Play-off meeting.
    \item Notify the League/Page Coordinators of re-scheduled games.
    \item Perform additional tasks as required; deemed necessary through the course of business.
\end{enumerate}

\subsubsection{B. Vice Chairperson}
\begin{enumerate}[1.]
    \item Attend all meetings, such as Board of Control, Executive Board, Screening, Protest Hearing, Appeals, Roster Review, Kick-off, Play-off Meetings at the CYC Office, etc.
    \item Sign and distribute all releases to all appropriate parties.
    \item Post and maintain a tracking record of all releases.
    \item Create and distribute sport kick-off “packets”
    \item Pass reschedule requests onto Rescheduler.
    \item Collect completed scorecards from various venues
    \item Create and maintain a Soccer Yellow/Red Card Report and distribute to all personnel at the Executive Board Meetings. Provide a copy to the Secretary to serve as an attachment to the EBM minutes.
    \item Create and maintain a Basketball Technical Foul Report and distribute to all personnel at the Executive Board Meetings. Provide a copy to the Secretary to serve as an attachment to the EBM minutes.
    \item Enter game scores into standings.
    \item Create and distribute any letters required for various reasons.  Provide a copy to the Secretary to serve as an attachment to the EBM minutes.
    \item Act as the District Chairperson when required by his/her absence.
    \item Shall ensure that a current copy of our Constitution, By-Laws and Rules is available on-line for the managers, coaches, spectators, etc. review/use. 
    \item Sign and seal Rosters and distribute to all of the appropriate parties.
    \item Sign and seal Supplemental Rosters and distribute to all of the appropriate parties.
    \item Review scorecards for all discrepancies and report results to the Executive Board at the monthly meetings.
    \item Maintain a record of all incident reports and distribute to all personnel at the Executive Board Meetings.
    \item Assist the Chairperson in all matters, in any way possible.
    \item Perform additional tasks as required; deemed necessary through the course of business.
\end{enumerate}

\subsubsection{C. Secretary}
\begin{enumerate}[1.]
    \item Record the attendance and create the minutes for the Executive Board Meetings.
    \item Distribute the minutes from Executive Board Meetings to all District personnel, to include the Chairperson, Vice Chairperson, Secretary, Treasurer, Special Advisor, Parish Representatives, Sport OICs, Past Chairpersons and the Webmaster for publication on the web site.
    \item Notify all appropriate personnel of all upcoming meeting(s)
    \item Process the Graham/LePage Scholarship Award
    \begin{enumerate}[A.]
        \item Distribute the nomination forms to all the Parish Representatives.
        \item Collect, process and submit the completed forms to the nomination review committee.
        \item Distribute the committee recommendations to the Parish Representatives for voting.
        \item Collect and tabulate the votes and award the scholarships to the winners at the May EBM.
    \end{enumerate}
    \item Record changes to the District Constitution and maintain the document with all appropriate changes.
    \item Send out mailings as requested by the Vice Chairperson.
    \item Collect the Parish Sport Coordinator‘s name and phone number for each sport season and compile a coordinators list.  Distribute this list at the EBM.
    \item Assist the Chairperson and Vice Chairperson in all matters, in any way possible.
    \item Perform additional tasks as required; deemed necessary through the course of business.
\end{enumerate}    

\subsubsection{D. Treasurer}
\begin{enumerate}[1.]
    \item Issue a statement each month to the Executive Board, reflecting the financial status of our organization.
    \item Issue all checks.
    \item Keep accurate records of all income and disbursements.
    \item Provide yearly summaries of comparisons of budget vs actual expenses.
    \item Ensure that the City of Florissant fee for field usage is divided equally among all teams participating in the given sport.
    \item Perform additional tasks as required; deemed necessary through the course of business.
\end{enumerate}

\subsubsection{E. Sergeant at Arms}
This is a position appointed by the Chairperson of a Past Chairperson.
\begin{enumerate}[1.]
    \item Enforce order and decorum as appropriate at Executive Board meeting.
    \item Request any meeting member to leave if he/she is disorderly or disruptive.
    \item Understand Roberts Rules of Order and how to apply them at Executive Board meetings.
\end{enumerate}

\subsection{Section 4: Official In Chief}
\begin{enumerate}[1.]
    \item Plan and hold clinics to teach the officials the rules of the sport.
    \item Assign officials to each game.
    \item Work with the District Rescheduler and Vice Chairperson to accomplish rescheduling of officials.
    \item Maintain a record of officials, showing name, age, telephone number, parish and years of experience.
    \item Keep a record of the games each official works.
    \item Report to the Executive Board, at the regular monthly meeting, the status of the sport in progress.
    \item Track and ensure District officials (for said sport) registered and paid for the “Official’s Fee”
    \item Post scores and maintain league standings, win/loss records of each team via review of scorecards.
    \item Maintain the official's uniform and equipment.  Order (through the Chairperson and Equipment Coordinator) any additional or replacement equipment.
    \item Observe the officials on the field of play and assist in the training of officials.  Also, enhance the skills/knowledge of officials.
    \item Provide an evaluation of each official at the end of each season.
    \item Pay scales/fees should be prepared by June. (see Section 6)
\end{enumerate}

\subsection{Section 5: Special Advisors}
\begin{enumerate}[1.]
    \item Will serve at the discretion of the Chairperson, and may include multiple assistants.
    \item Will support the Chairperson, the Vice Chairperson, and Sports Coordinators in their efforts to perform their tasks as outlined in the Constitution.
    \item Will report directly to the Chairperson in all areas assigned to him/her.
    \item Will apply to the Florissant Park Department for playing field permits.
    \item Obtain Field Time from the Florissant Parks Department for rescheduled games
\end{enumerate}

\subsection{Section 6: Pay Scales}
Pay scale/fees for Officials, Gym Guards, Facility Rental and Usage are presented in June and voted on at the July District Executive Board meeting, to become effective with the Soccer/Volleyball season.

\subsection{Section 7: Tournaments}
Participation by any team of the North County CYC in any tournament, pre-season, in-season or post-season, must be on a non-interference basis.  Games of the North County District must take precedence over a tournament game.

\subsection{Section 8: Support to the Archdiocesan CYC}
\begin{enumerate}[A.]
    \item A fee for all teams eligible to participate in the Archdiocesan Championship Playoffs, for all non-Playoff teams and each golf team, with golf having Spring and Fall seasons, and each lacrosse team shall be paid to the St. Louis Archdiocesan CYC Athletic Association for each sport season.  Individual fees shall be negotiated/established for each of these categories and approved by the Executive Board.
    \item One (1) copy of all rosters, manager/coach accreditation form and schedules are to be furnished to the Archdiocesan Office.
    \item All requirements above, are to be submitted before completion of the third week of each sport season.
\end{enumerate}

\subsection{Section 9: Excess Funds}
While we budget to avoid having excess money in the treasury, if after the close of the baseball/softball season, an audit reveals that excess money does in fact exist, the excess shall be refunded or credited to member Athletic Associations in direct proportion to their assessed fees during the previous year.

\subsection{Section 10: Executive Board Identification Card}
Each member of the Executive Board shall be issued a card by the District Chairperson, for identification purposes, should the need arise. 

\subsection{Section 11: Screening Committee}
\begin{enumerate}[A.]
    \item The Screening Committee is only an advisory function to the Scheduling Committee.
    \item The Chairperson, or the Vice Chairperson may chair the Screening Meeting.
    \item The committee shall meet within 7-10 days after Team Entry Form submittal and before the last day to add/drop a team.
    \item Attendance at the Screening Meeting is limited to the Screening Committee Chairperson, members of the Scheduling Committee and representatives from each parish (sport-in-season coordinators and Parish Representatives). The Screening Committee Chairperson shall take attendance.  Failure to have any representative present means that the remainder of the Screening Committee will act in that athletic association’s behalf.
    \item Failure to have completed Team Entry Forms submitted to the pre-screening group on time, could, at the discretion of the Screening Committee, cause the teams to be screened without additional inputs from the tardy athletic association.  Completed forms shall include the signature of the Parish Representative/Sport Coordinator. Should information presented on the cards be considered misleading by the Screening Committee, they shall have the prerogative of accepting their own interpretation.  Any deliberate attempt by an athletic association, in presenting Team Entry Form data or in their oral presentation at the Screening Meeting, to circumvent the intended purpose of establishing leagues of comparable competitiveness, may result in that athletic association’s team forfeiting their rights to winning the league.  A simple majority of the Executive Board will be required to enforce this last action.  The Athletic Association screening representative(s) may also be subject to disciplinary measures by the Executive Board.
    \item Implement the following guidelines for the Screening Committee activities so as to maximize, in as expeditious a manner as possible, the process leading to the formation of leagues of comparable competitiveness:
    \begin{enumerate}[1.]
        \item Have screening committee verify data presented on the Team Entry Forms at the Screening Meeting.
        \item NO parish may be forced to place two (2) teams in the same league unless they agree and can verify that the team makeup is based on ability and not random selection.
        \item A team may not be dropped, and new team added of same within the same league or division. District will reassign the players.
        \item Any major change in team structure, before the Screening Meeting, will require a NEW TEAM ENTRY FORM, before the meeting starts.
    \end{enumerate}
    \item There will be no more than two (2) ``A'' leagues within any age group, either Open or Closed.  The ``A1'' League will be the strongest league in a given division.  Atom and Bantam Leagues do NOT have “A” Leagues.
    \item The team designation of Open or Closed shall not be changed after the Screening Meeting.
\end{enumerate}

\subsection{Section 12: Executive Board Meeting Attendance}
Anyone may attend an Executive Board meeting.  However, in order to participate, notice must be entered on the meeting agenda or the District Chairperson shall be notified 48 hours prior to the scheduled meeting.

\subsection{Section 13: Team Withdrawal}
An athletic association may withdraw a team, with no penalty, anytime prior to the last day to add/drop a team as designated by the District Chairperson.  If withdrawn anytime after this designated date, the athletic association will still be charged for the team's entry fee.


    
    
    

\backmatter

